Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-17 paper.tex
psom execution

        To execute a pipeline, the user must provide the pipeline structure and
the pipeline configuration options. The latter consists of the log
directory and the pipepline execution modes (e.g., session, background, batch,
qsub, msub).

>>>>

        To execute a pipeline, the user must provide the pipeline structure and
the pipeline configuration options. The latter consists of the log
directory, which must be provided, and the pipepline execution modes (e.g., session, background, batch,
qsub, msub), in which the default mode is \textit{background}. Pipeline
execution is achieved through the execution of the \textit{psom\_run\_pipeline}
command.

        Pipeline execution is broken down into three distinct modules: 1)
initialization stage, 2) pipeline manager and 3) job manager. The initialization
stage performs some checks to ensure that the pipeline can execute successfully
(e.g., verify that pipeline is a DAG, check that output files are generated only
once, check that all input files not generated by the pipeline exist on disk,
delete any already existing output files), as well as performance checks (e.g.
do not recompute pipeline steps that have already been executed, create
necessary output folders to avoid creating them for each individual job). The
initialization manager can determine which jobs need to be executed by comparing
the current pipeline jobs with the details of those previously executed stored
in the logs folder. The jobs that have been executed can have the following
states: 1) none, 2) finished and 3) failed. The initialization manager stage the jobs 
with a \textit{none} or \textit{failed} status for recomputation. For jobs whose
description has changed since the previous \textit{finished} execution, the
initialization will also stage it for recomputation. Should the user want to
reexecution a previously executed \textit{finished} job, the user may force
reexecution by setting \textit{opt\_pipe.restart} parameter to include all jobs
to be reexecuted.

        The pipeline manager is responsible for monitoring the state of the
pipeline and submitting jobs for execution. Its duties begin after the
initialization manager has completed execution. Jobs can be submitted by the
pipeline manager once all their dependencies have been satisfied. The
dependencies of a job are designated as met if there are none or when its parent jobs within the
dependency graph are tagged as \textit{finished}. In addition, a job is
considered to be successfully completely when all the dependencies of its
children jobs have been satisfied. Depending on the pipeline configuration,
there may be a limit to how many jobs can run in parallel. Once a job has
finished executing, an empty tag file is created with a filename containing the
final state in the logs folder. The pipeline manager continuously parses through
the logs folder in search of these state files to delete and update the history
file with the job state.

        Every time a job is submitted by the pipeline manager for execution, a
job manager is started. It is a Matlab function responsible for creating the job
profile and generating the job-specific logs and the job exit tags. When
the job terminates, the job manager will verify that all output has been
correctly generated and assigns a job tagged based on this verification that
will be reported back to the pipeline manager.
